Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-12 paper/ijcai/paper.tex
guideline added
sketching abstract and polishing intro

\title{Reassessing the Impact of Dynamic Slicing in SFL}

@@

\begin{abstract}
  \Sof{@todo} 
\end{abstract}

@@

This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} different programs comprised in the 
Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
used to evaluate fault localization research. The intuition for the
\comb{} combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Prior
work reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}
but they used a non-representative set of subjects in their evaluation
or used less rigorous methods to assess improvement of techniques compared to those used
today~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more accurate metric and a larger
dataset. The D4J dataset is about twice as large than the biggest test
suite used in previous studies. It is worth noting that Automated
Program Repair techniques should directly benefit from these results---either to
improve their results or to be aware they should not invest on this
integration. This study covers the following research questions:

@@

The first question addresses an important problem associated with
dynamic slicing techniques---that of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
important problem happens in our experiments. The second research
questions effectively evaluates the impact of the combination. To sum,
our results show that \Sof{@todo: sum up the results}.

The contributions of this work are as follows \Sof{Finish this}:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
	%\item Empirical evidence that the \comb{} combination improves 
\end{itemize}

@@

As in other recent related studies, we used the \dfj{} benchmark in
our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library that provides a set of helper utilities for the
     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
     of self-contained mathematics and statistics components. The
     \closure{} is a toolset for turning JavaScript files into smaller
     scripts for faster download and execution in the
     browser. \chart{} is a Java library for creating charts. \jtime{}
     is a lightweight library that aims to replace the default Java
     {\small\texttt{java.util.Date}} classes providing simpler
     APIs. \mockito{} is a mocking testing framework.\comments{ that
       enables the developer to simulate the behavior of classes that
       cannot be used in unit testing.}

@@

@@

        \lang{}            &  & \\ 	
        \cmath{}           &  & \\
        \closure{}          &  & \\	
		\chart{}			& 59.30\% & 53.64\% \\ 	
        \jtime{}            & 17.27\% & 32.92\%\\	
        \mockito{}          & 16.99\% & 21.67\%\\

@@

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
  \label{table:fsws}
\end{table*}

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
		\midrule
		$<0$  & 31.87\% & 25.27\% \\ 
		$=0$  & 26.37\% & 26.37\% \\ 
		$>0$  & 41.76\% & 41.76\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
	\label{tab:diagnosis}
\end{table}
\normalsize

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
Mean & 521.59     & 855.34   & 758.06    \\ \midrule
Median & 57.21      & 260.33                & 109                \\ \midrule
Variance & 1021.65      & 1307.70   & 1275.34    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.56 \\ p-value = 4.00 x $10^{-15}$} & \makecell{W = 0.69 \\ p-value = 1.81 x $10^{-12}$} & \makecell{W = 0.65 \\ p-value = 1.68 x $10^{-13}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 7.22 \\ p-value = 0.027}} \\ 
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
  \label{table:st}
\end{table*}

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
		\label{fig:performance}
\end{figure}

@@

>>>>

\title{Demystifying the Dynamic Slicing and SFL Combination}

@@

\begin{abstract}
  The task of locating faulty code from failing testing is a very
  important problem known as software fault localization. This paper
  reports on a comprehensive study to reassess the impact of combining
  two very popular techniques to that end--Dynamic Slicing and
  Spectrum-based Fault Localization. Our results show that \Fix{...}
\end{abstract}

@@

This paper reports the results of a comprehensive study evaluating the
impact of combining \ds{} and \sfl{} to improve software fault
localization. The intuition for the \comb{} combination is that
several highly ranked statements, albeit covered by failing
executions, may be unrelated to the fault. The study involves
\numFaults{} faults from \numPrograms{} different programs comprised
in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
is frequently used to evaluate fault localization research. Prior work
reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
but they used a non-representative set of subjects in their evaluation
or used arcaic methods to evaluate technique
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more rigorous experimental
methodology and a larger dataset.\comments{ The D4J dataset is about
  twice as large than the biggest test suite used in previous
  studies.} This study covers the following research questions:

@@

The first question addresses the important problem of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
issue manifests in our experiments. The second research questions
effectively evaluates the impact of the combination. To sum, our
results show that \Sof{@todo: sum up the results}.

The contributions of this work are as follows \Sof{Finish this}:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
   \item A tool that implements \comb{}.
	%\item Empirical evidence that the \comb{} combination improves 
\end{itemize}

@@

As in other recent related studies, we used the \dfj{} benchmark in
our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library that provides a set of helper utilities for the
     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
     of self-contained mathematics and statistics components. The
     \closure{} is a toolset for turning JavaScript files into smaller
     scripts for faster download and execution in the
     browser. \chart{} is a Java library for creating charts. \jtime{}
     is a lightweight library that aims to replace the default Java
     {\small\texttt{java.util.Date}} classes providing simpler
     APIs. \mockito{} is a mocking testing framework.

@@

\Sof{Parei Aqui}

@@

        \lang{}            & 0.77\% & 30.28\%\\ 	
        \cmath{}           &  & \\
        \closure{}          &  & \\	
		\chart{}			& 59.30\% & 53.64\% \\ 	
        \jtime{}            & 17.27\% & 32.92\%\\	
        \mockito{}          & 16.99\% & 21.67\%\\

@@

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\   
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
  \label{table:fsws}
\end{table*}

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
		\midrule
		$<0$  & 20.00\% & 17.42\% \\ 
		$=0$  & 47.10\% & 37.42\% \\ 
		$>0$  & 32.90\% & 45.16\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
	\label{tab:diagnosis}
\end{table}
\normalsize

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
Mean & 387.46     & 576.74   & 522.35   \\ \midrule
Median & 44.50      & 48.25               & 46.00                \\ \midrule
Variance & 827.80      & 1075.90   & 1275.34    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.51 \\ p-value = 9.65 x $10^{-21}$} & \makecell{W = 0.59 \\ p-value = 5.29 x $10^{-19}$} & \makecell{W = 0.56 \\ p-value = 8.95 x $10^{-20}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 16.87 \\ p-value = 2.2 x $10^{-4}$}} \\ 
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
  \label{table:st}
\end{table*}

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
		\label{fig:performance}
\end{figure}

@@

\Mar{moved from intro$\rightarrow$} It is worth noting that Automated
Program Repair techniques should directly benefit from these
results---either to improve their results or to be aware they should
not invest on this integration.
